\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}

\title{Project Plan}
\author{Mill Luangamornlert}

\begin{document}
\maketitle
Abstract - Note and thanks for the project
\section{Introduction}
Introducing the project and what machine learning and data science is.

\subsection{Dataset}
Introducing the Lahman dataset and the R package as well as explaining some terms from baseball -(Look into improving communications with fewest words)

\section{Simple stuff}
\subsection{regression}
Basic introduction to linear and logistical regression since we will be able to refer from SC2/SM3. 

\textbf{Note}: Look into what level of maths is necessary to convey information while leaving enough space

\subsubsection{example}
basic example of atbats vs hits (explain!)

\subsection{classification}
Look into logistic regression and sorting categorically.
Maths on sigmoid function.
Maths on estimating betas using MLE - (needed)

\subsubsection{example}
multiple logistic regression on playoff
Look into adding prediction based on modern data

\section{Trees}
Explain what a tree is and with diagrams. \\
Explaining Entropy

\subsection{regression}

\subsection{classification}

\section{Bagging/Boosting}
\textbf{Note}: \textit{Still deciding if to do Bagging due to space and aim to do boosting but may introduce bagging briefly if space permits}

Boosting, looking at AdaBoost and Gradient Boosting Classifiers (XGBoost or LightGBM)


\section{What I have done}
Read methods of machine learning from ISLR and ESL.

Looking into building up into additive models based on learning. Have done basic things on Linear Regression but should rewrite it out. Logistic Regression, looked at the sigmoid equation already. 

Looked into trees and starting looking at entropy, gini and information gain.

Coded linear regression and logistic regression about to look into decision trees.

Have the basic algorithm for boosting down but need to go into detail for each one and build on from there


\section{what to do}
Coding it all, and start the writeup as I research along.


\end{document}